\large COOPERATIVE 3-D MAP GENERATION USING MULTIPLE UAVS

### 2015-04-25 draft.tex
Changing font.

\documentclass[letterpaper, oneside, 12pt]{report}
\usepackage[margin = 1.0in]{geometry}
\usepackage[nottoc,notlof,notlot]{tocbibind}
\usepackage[colorlinks=false]{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{cite}
\usepackage{fontspec}
\setmainfont{Tahoma}

\geometry{letterpaper}

@@

% Title page parameters
\lhead{Andrew Lawson}
\title{\large COOPERATIVE CONTROL OF MULTIPLE UAVS FOR 3-D MAP GENERATION}
\author{
  \large
  Andrew Lawson \\
  University of Connecticut \\
  Computer Science and Engineering
}
\date{\large May 1, 2015}
\pagestyle{fancy}

@@

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
 Thanks Mum!
\end{abstract}
\clearpage

@@

\begin{table}[h!]
\centering
\caption{List of Components}
\vspace{2mm}
\begin{tabular}{l l}
\hline \hline
\vspace{-2mm}
Component & \multicolumn{1}{l}{Description} \\ [1ex]
\hline
& \\
Pandaboard ES & High-level Computer \\
DJI Naza & Low-level computer \\
Arduino Uno & I/O controller \\
Microsoft Kinect & Visual sensor \\
MaxSonar EZ0	& Sonar sensor \\
Xbee & Wireless communication
\end{tabular}
\end{table}

>>>>

\documentclass[letterpaper, oneside, 12pt]{report}
\usepackage[margin = 1.0in]{geometry}
\usepackage[nottoc,notlof,notlot]{tocbibind}
\usepackage[colorlinks=false]{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{cite}
\usepackage{newcent}

\geometry{letterpaper}
\renewcommand{\familydefault}{\sfdefault}

@@

% Title page parameters
\lhead{Andrew Lawson}
\title{\large COOPERATIVE 3-D MAP GENERATION USING MULTIPLE UAVS}
\author{
  \large
  Andrew Lawson \\
  University of Connecticut \\
  Computer Science and Engineering
}
\date{\large May 1, 2015}
\pagestyle{fancy}

@@

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
 I'd like to thank Prof. Shalabh Gupta, Prof. Ashwin Dani, and Prof. Robert McCartney for their advice and support. I'd also like to thank Kris Balisciano, Chung Yang, and everyone in L.I.N.K.S. Lab for all their work on the project.
\end{abstract}
\clearpage

@@

\begin{table}[h!]
\centering
\caption{List of Components}
\vspace{2mm}
\begin{tabular}{l l}
\hline \hline
\vspace{-2mm}
Component & \multicolumn{1}{l}{Description} \\ [1ex]
\hline
& \\
ODROID XU3 & ARM SBU \\
Pixhawk PX4 & Controller \\
Microsoft Kinect & Visual Sensor \\
MaxSonar EZ0	& Sonar Sensor \\
\end{tabular}
\end{table}
